A community-maintained standard library of population genetic models

### 2020-05-12 popSimManu.tex
Update model table with results and fix references.

\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the catalog and summary of computing resources needed for simulation.
For each model, we report the CPU time, maximum memory usage and the
size of the output \tskit file, as simulated using the \texttt{msprime} simulation engine.
In each case, we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single run on an Intel i5-7600 CPU.
Computing resources required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

We validated our implementation of the \texttt{SLiM} engine by comparing
estimates of several population genetic summary statistics for neutral simulations generated by both \texttt{SLiM}
and \texttt{msprime}.
Examples of this validation for the AncientEurasia\_9K19 model \citep{AncientEurasia 9K19}
are shown in Figures \ref{fig:slim_val_map} and \ref{fig:slim_val_nomap}.
For this model,
down-scaling factors of up to $50$ produce patterns of both diversity and linkage disequilibrium that are
very similar to those observed under the coalescent (i.e., \texttt{msprime}), when both are simulated using the HapMapII\_GRCh37 recombination map
(Figure \ref{fig:slim_val_map}),
although the distribution of Tajima's $D$ differs slightly when scaling down by a factor of $50$.
%likely due to the subtle differences produced by down-scaling.
Interestingly, the effects of down-scaling are more prominent and extend to other sequence-based statistics
when data sets are simulated under a uniform recombination rate (Figure \ref{fig:slim_val_nomap}).
Importantly, both comparisons validate the equivalence of \texttt{SLiM} and \texttt{msprime} when no down-scaling is applied.
The results are also optimistic about the rescaling strategy to reduce computational burden,
but the possible effects are not well-understood,
so results relying on rescaled simulations should be carefully validated.

>>>>

\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the catalog and summary of computing resources needed for simulation.
For each model, we report the CPU time, maximum memory usage and the
size of the output \tskit file, as simulated using the \texttt{msprime} simulation engine.
In each case, we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single run on an Intel i5-7600K CPU.
Computing resources required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

We validated our implementation of the \texttt{SLiM} engine by comparing
estimates of several population genetic summary statistics for neutral simulations generated by both \texttt{SLiM}
and \texttt{msprime}.
Examples of this validation for the AncientEurasia\_9K19 model
\citep{kamm2019efficiently}
are shown in Figures \ref{fig:slim_val_map} and \ref{fig:slim_val_nomap}.
For this model,
down-scaling factors of up to $50$ produce patterns of both diversity and linkage disequilibrium that are
very similar to those observed under the coalescent (i.e., \texttt{msprime}), when both are simulated using the HapMapII\_GRCh37 recombination map
(Figure \ref{fig:slim_val_map}),
although the distribution of Tajima's $D$ differs slightly when scaling down by a factor of $50$.
%likely due to the subtle differences produced by down-scaling.
Interestingly, the effects of down-scaling are more prominent and extend to other sequence-based statistics
when data sets are simulated under a uniform recombination rate (Figure \ref{fig:slim_val_nomap}).
Importantly, both comparisons validate the equivalence of \texttt{SLiM} and \texttt{msprime} when no down-scaling is applied.
The results are also optimistic about the rescaling strategy to reduce computational burden,
but the possible effects are not well-understood,
so results relying on rescaled simulations should be carefully validated.
